---
title: "R Notebook"
output: html_notebook
---

# Merged_Donors

## Pre-processing:

What to filter out:

-   cells expressing \<500 genes

-   cells expressing \>20% MT genes

-   \<1000 gene counts

-   genes expressed in fewer than 10 cells

```{r,collapse = TRUE}
library(Seurat)
library(tidyverse)
library(patchwork)
library(sctransform)
library(ggplot2)
message("libs loaded")


options(future.globals.maxSize = 16 * 1024^3)  # 16 GB

# Load the PBMC datasets
Donor5_D0.data <- Read10X(data.dir = "/Users/jamiechoe/Desktop/PracticeRNA/jamie_project/RawData/PWH26D0")
Donor5_D1.data <- Read10X(data.dir = "/Users/jamiechoe/Desktop/PracticeRNA/jamie_project/RawData/PWH26D1")
Donor4_D0.data <- Read10X(data.dir = "/Users/jamiechoe/Desktop/PracticeRNA/jamie_project/RawData/PWH27D0")
Donor4_D1.data <- Read10X(data.dir = "/Users/jamiechoe/Desktop/PracticeRNA/jamie_project/RawData/PWH27D1")
Donor3_D0.data <- Read10X(data.dir = "/Users/jamiechoe/Desktop/PracticeRNA/jamie_project/RawData/PWH28D0")
Donor3_D1.data <- Read10X(data.dir = "/Users/jamiechoe/Desktop/PracticeRNA/jamie_project/RawData/PWH28D1")

# Create objects. Filter out cells expressing <500 genes, and genes expressed in < 10 cells. 
Donor5_D0 <- CreateSeuratObject(counts = Donor5_D0.data, project = "Donor5_Day0", min.cells = 10, min.features = 500)
Donor5_D1 <- CreateSeuratObject(counts = Donor5_D1.data, project = "Donor5_Day1",min.cells = 10, min.features = 500)
Donor4_D0 <- CreateSeuratObject(counts = Donor4_D0.data, project = "Donor4_Day0",min.cells = 10, min.features = 500)
Donor4_D1 <- CreateSeuratObject(counts = Donor4_D1.data, project = "Donor4_Day1",min.cells = 10, min.features = 500)
Donor3_D0 <- CreateSeuratObject(counts = Donor3_D0.data, project = "Donor3_Day0",min.cells = 10, min.features = 500)
Donor3_D1 <- CreateSeuratObject(counts = Donor3_D1.data, project = "Donor3_Day1",min.cells = 10, min.features = 500)

Donor5_D0[["percent.mt"]] <- PercentageFeatureSet(Donor5_D0, pattern = "^MT-")
Donor5_D1[["percent.mt"]] <- PercentageFeatureSet(Donor5_D1, pattern = "^MT-")
Donor4_D0[["percent.mt"]] <- PercentageFeatureSet(Donor4_D0, pattern = "^MT-")
Donor4_D1[["percent.mt"]] <- PercentageFeatureSet(Donor4_D1, pattern = "^MT-")
Donor3_D0[["percent.mt"]] <- PercentageFeatureSet(Donor3_D0, pattern = "^MT-")
Donor3_D1[["percent.mt"]] <- PercentageFeatureSet(Donor3_D1, pattern = "^MT-")


#Create list of objects
DonorList = list(Donor5_D0,Donor5_D1,Donor4_D0,Donor4_D1,Donor3_D0,Donor3_D1)
message("List created")

#Filtering out each object
DonorList <- lapply(DonorList, function(obj) {
  subset(obj, subset = nCount_RNA > 1000 & percent.mt < 20)})
message("Filering each object finished!")

#Using SCTransform on each object
Merged_Donors <- lapply(X = DonorList, FUN = SCTransform, vst.flavor = "v2", vars.to.regress = "percent.mt")
message("SCTransform Finished!")

#Integration
features <- SelectIntegrationFeatures(object.list = Merged_Donors, nfeatures = 3000)
Merged_Donors <- PrepSCTIntegration(object.list = Merged_Donors, anchor.features = features)
message("Integration prepped, finding anchors now.")

#Anchors
DonorAnchors <- FindIntegrationAnchors(object.list = Merged_Donors, normalization.method = "SCT", anchor.features = features)
#saveRDS(DonorAnchors,"/Users/jamiechoe/Desktop/PracticeRNA/jamie_project/Merged_Donors/Merged_1_Anchors.rds") 
#(Only enable if you want to save the ancors)

message("Anchors made and saved")

Merged_Donors <- IntegrateData(anchorset = DonorAnchors, normalization.method = "SCT")
message("Integration complete.")

#Run PCA to find PCs
Merged_Donors <- RunPCA(Merged_Donors, verbose = FALSE)
saveRDS(Merged_Donors, "/Users/jamiechoe/Desktop/PracticeRNA/jamie_project/Merged_Donors/Merged_Donors.rds")
message("Finished running PCA")

#Creating Elbowplot
EP <- ElbowPlot(Merged_Donors)
ggsave("/Users/jamiechoe/Desktop/PracticeRNA/jamie_project/Merged_Donors/Merged_1_Elbow", plot = EP, width = 8, height = 6)
message("Elbowplot created and saved")
```

```{r}
library(openxlsx) 
library(Seurat)
library(tidyverse)
library(patchwork)
library(sctransform)
library(ggplot2)
message("libs loaded")

Merged_Donors <- readRDS("/Users/jamiechoe/Desktop/PracticeRNA/jamie_project/Merged_Donors/Merged_Donors.rds")

# Process the data

#Setting dims = 11
Merged_Donors <- RunUMAP(Merged_Donors, reduction = "pca", dims = 1:11)

Merged_Donors <- FindNeighbors(Merged_Donors, reduction = "pca", dims = 1:11)

#Resolutions 

#Doing three resolutions to see which one is best. 
Merged_Donors <- FindClusters(Merged_Donors, resolution = 0.5)
Merged_Donors <- FindClusters(Merged_Donors, resolution = 0.1)
Merged_Donors <- FindClusters(Merged_Donors, resolution = 0.05)


# Umaps
dim_plots <- list(
  DimPlot_clusters0.5 = DimPlot(Merged_Donors, reduction = "umap", group.by = "integrated_snn_res.0.5") + ggtitle("Resolution 0.5"),
  DimPlot_clusters0.1 = DimPlot(Merged_Donors, reduction = "umap", group.by = "integrated_snn_res.0.1") + ggtitle("Resolution 0.1"),
  DimPlot_clusters0.05 = DimPlot(Merged_Donors, reduction = "umap", group.by = "integrated_snn_res.0.05") + ggtitle("Resolution 0.05")
)

message("UMAPs created!")

#Saving the UMAPs

#PDF
for (plot_name in names(dim_plots)) {
  ggsave(paste0("/Users/jamiechoe/Desktop/PracticeRNA/jamie_project/Merged_Donors/", plot_name, ".pdf"), 
         plot = dim_plots[[plot_name]], 
         width = 8, height = 6)}

#PNG
for (plot_name in names(dim_plots)) {
  ggsave(paste0("/Users/jamiechoe/Desktop/PracticeRNA/jamie_project/Merged_Donors/", plot_name, ".png"), 
         plot = dim_plots[[plot_name]], 
         width = 8, height = 6)}

message("UMAPs saved")


#FindAllMarkers!
Merged_Donors <- PrepSCTFindMarkers(Merged_Donors)


Markers0.5 <- FindAllMarkers(Merged_Donors, assay = "SCT", min.pct = 0.25, logfc.threshold = 0.25, group.by = "integrated_snn_res.0.5")
write.xlsx(Markers0.5,"/Users/jamiechoe/Desktop/PracticeRNA/jamie_project/Merged_Donors/MergedMarkers_0.5.xlsx")

Markers0.1 <- FindAllMarkers(Merged_Donors, assay = "SCT", min.pct = 0.25, logfc.threshold = 0.25, group.by = "integrated_snn_res.0.1")
write.xlsx(Markers0.1,"/Users/jamiechoe/Desktop/PracticeRNA/jamie_project/Merged_Donors/MergedMarkers_0.1.xlsx")

Markers0.05 <- FindAllMarkers(Merged_Donors, assay = "SCT", min.pct = 0.25, logfc.threshold = 0.25, group.by = "integrated_snn_res.0.05")
write.xlsx(Markers0.05,"/Users/jamiechoe/Desktop/PracticeRNA/jamie_project/Merged_Donors/MergedMarkers_0.05.xlsx")
message("Find All Markers Finished and Saved")


#Save Object
saveRDS(Merged_Donors, "/Users/jamiechoe/Desktop/PracticeRNA/jamie_project/Merged_Donors/Merged_Donors.rds")

message("obj saved")
```

## Analyzing Merged_Donors

#### Keratinicyte 1 - KRT1

```{r}
cluster0.markers <- FindMarkers(Merged_Donors, ident.1 = 0, only.pos = TRUE)
head(cluster0.markers, n = 15)
```

**KRT1:** provides instructions for making keratin 1.

**TIMP1:** upregulated in keratinocytes during inflammation. Can affect cell proliferation and tissue remodeling.

```{r}
FeaturePlot(Merged_Donors, features = c("KRT1"), cols = c("lightgrey", "#f7766dff"))
```

#### Keratinocyte 2 - KRT14

```{r}
cluster1.markers <- FindMarkers(Merged_Donors, ident.1 = 1, only.pos = TRUE)
head(cluster1.markers, n = 15)
```

**KRT14:** encodes for keratin 14. Provides structural support for the keratinocytes.

**ITGA6, ITGA3, ITGA2:** helps keratinocytes attach to the basement membrane beneath the epidermis.

```{r}
FeaturePlot(Merged_Donors, features = "KRT14", cols = c("lightgrey","#d49200ff"))
```

#### Fibroblast - COL1A1

```{r}
cluster2.markers <- FindMarkers(Merged_Donors, ident.1 = 2, only.pos = TRUE)
head(cluster2.markers, n = 15)
```

**COL1A1:** provides the instructions for producing type I collagen. Fibroblasts rely heavily on COL1A1.

**MMP2:** released by fibroblasts, and is a key enzyme in the breakdown of ECM components.

```{r}
FeaturePlot(Merged_Donors, features = "COL1A1", cols = c("lightgrey","#94aa01ff"))
```

#### Myeloid - LYZ

```{r}
cluster3.markers <- FindMarkers(Merged_Donors, ident.1 = 3, only.pos = TRUE)
head(cluster3.markers, n = 15)
```

**LYZ:** Produced and released by myeloid cells, serves as crucial for the immune system. **TYROBP:** plays a crucial role in myeloid cell activation and immune responses.

```{r}
FeaturePlot(Merged_Donors, features = "LYZ", cols = c("lightgrey","#03bb38ff"))
```

#### Lymphoid - CD3D

```{r}
cluster4.markers <- FindMarkers(Merged_Donors, ident.1 = 4, only.pos = TRUE)
head(cluster4.markers, n = 15)
```

**CD3D:** involved in T-cell development and signal transduction

```{r}
FeaturePlot(Merged_Donors, features = "CD3D", cols = c("lightgrey","#03c19fff"))
```

#### Mast - TPSAB1

```{r}
cluster5.markers <- FindMarkers(Merged_Donors, ident.1 = 5, only.pos = TRUE)
head(cluster5.markers, n = 15)
```

**TPSAB1:** codes for tryptase, a protein that is highly concentrated in mast cells.

```{r}
FeaturePlot(Merged_Donors, features = "TPSAB1", cols = c("lightgrey","#00bae3ff"))
```

#### Endothelial - PECAM1

```{r}
cluster6.markers <- FindMarkers(Merged_Donors, ident.1 = 6, only.pos = TRUE)
head(cluster6.markers, n = 15)
```

**PECAM1:** expressed by endothelial cells, maintain the integrity of endothelial cell junctions.

```{r}
FeaturePlot(Merged_Donors, features = "PECAM1", cols = c("lightgrey","#629dffff"))
```

#### Pericyte - ACTA2

```{r}
cluster7.markers <- FindMarkers(Merged_Donors, ident.1 = 7, only.pos = TRUE)
head(cluster7.markers, n = 15)
```

```{r}
FeaturePlot(Merged_Donors, features = "ACTA2", cols = c("lightgrey","#db71fbff"))
```

#### Melanocytes - TYRP1

```{r}
cluster8.markers <- FindMarkers(Merged_Donors, ident.1 = 8, only.pos = TRUE)
head(cluster8.markers, n = 15)
```

```{r}
FeaturePlot(Merged_Donors, features = "TYRP1", cols = c("lightgrey","#ff61c3ff"))
```

## FindALLMarkers

Creates new variable called Merged_Donors_Markers that is the unfiltered markers for Merged_Donors.

```{r}
Merged_Donors_Markers = FindAllMarkers(Merged_Donors, logfc.threshold = 0.25, min.pct = 0.25)

#Create new column
Merged_Donors_Markers$min.pct.diff = (Merged_Donors_Markers$pct.1 - Merged_Donors_Markers$pct.2)
#Order in descending order
Merged_Donors_Markers = Merged_Donors_Markers[order(Merged_Donors_Markers$min.pct.diff, decreasing = TRUE),]  
#Print the first 20 rows of the table
head(Merged_Donors_Markers, n = 20)

#Save Matrix to excel
install.packages("writexl")
library("writexl") 

write_xlsx(Merged_Donors_Markers,"UnfilteredMarkers.xlsx",col_names = TRUE,format_headers = TRUE)
```

## Creating UMAP

Creates a labeled UMAP. Also re-labels the Idents of Merged_Donors.

```{r}
#Assigns IDs
Labeled_UMAP.ids <- c("Keratinocyte 1","Keratinocyte 2","Fibroblasts","Myeloid","Lymphoid","Mast","Endothelial","Pericytes","Melanocytes")

#Names each level of Merged_Donors
names(Labeled_UMAP.ids) <- levels(Merged_Donors)
Merged_Donors <- RenameIdents(Merged_Donors, Labeled_UMAP.ids)
DimPlot(Merged_Donors, reduction = "umap", label = TRUE, pt.size = 0.5) + NoLegend()
ggsave(filename = "/Users/jamiechoe/Desktop/PracticeRNA/jamie_project/Merged_Donors/LabeledUMAP.png", height = 4, width = 8)
```

integrated UMAP - Creates a UMAP that shows the day that sample was taken. Demonstrates the success of integration.

```{r}

Merged_Donors$day <- ifelse(grepl("Day0", Merged_Donors$orig.ident), "D0", "D1")

DimPlot(Merged_Donors, group.by = "day", label = TRUE) + ggtitle("D0 vs. D1")
```

## Violin Plot

```{r}
violin_genes = c("KRT1", "ITGA6","MMP2","LYZ","CD3D","TPSAB1","PECAM1","MYH11","TYR")
VlnPlot(object = Merged_Donors, features = violin_genes, stack = TRUE)
```

------------------------------------------------------------------------

# Myeloid

## Pre-processing

```{r}

library(Seurat)
library(tidyverse)
library(dplyr)
library(patchwork)
library(SeuratObject)

Merged_Donors <- readRDS("/Users/jamiechoe/Desktop/PracticeRNA/jamie_project/Merged_Donors/Merged_Donors.rds")

#Subsetting from Merged Donors to isolate Myeloid cluster
MyeloidCluster <- subset(x = Merged_Donors, idents = c("Myeloid"))

MyeloidCluster <- SplitObject(MyeloidCluster, split.by = "day")

#Using SCTransform
MyeloidCluster <- lapply(MyeloidCluster, SCTransform, vst.flavor = "v2")
message("SCTransform Finished!")

#Integration
features <- SelectIntegrationFeatures(object.list = MyeloidCluster, nfeatures = 3000)
MyeloidCluster <- PrepSCTIntegration(object.list = MyeloidCluster, anchor.features = features)
message("Integration prepped, finding anchors now.")

#Anchors
DonorAnchors <- FindIntegrationAnchors(object.list = MyeloidCluster, normalization.method = "SCT", anchor.features = features)
#saveRDS(DonorAnchors, "/Users/jamiechoe/Desktop/PracticeRNA/jamie_project/Myeloid_Subcluster/Myeloid_Anchors.rds")
message("Anchors made and saved")

MyeloidCluster <- IntegrateData(anchorset = DonorAnchors, normalization.method = "SCT")
message("Integration complete.")


#Run PCA to find PCs
MyeloidIntegrated <- RunPCA(MyeloidCluster)
#saveRDS(MyeloidCluster, "/Users/jamiechoe/Desktop/PracticeRNA/jamie_project/Myeloid_Subcluster/MyeloidIntegrated.rds")
message("Finished running PCA")

#Creating Elbowplot
ElbowPlot(MyeloidIntegrated)
```

```{r}
install.packages("openxlsx", dependencies = TRUE)
library(openxlsx)
library(writexl)

MyeloidCluster <- readRDS("/Users/jamiechoe/Desktop/PracticeRNA/jamie_project/Myeloid_Subcluster/MyeloidIntegrated.rds")


# Process the data
MyeloidIntegrated <- RunUMAP(MyeloidIntegrated, reduction = "pca", dims = 1:11)

MyeloidIntegrated <- FindNeighbors(MyeloidIntegrated, reduction = "pca", dims = 1:11)


#Resolutions 
MyeloidIntegrated <- FindClusters(MyeloidIntegrated, resolution = 0.5)
MyeloidIntegrated <- FindClusters(MyeloidIntegrated, resolution = 0.4)
MyeloidIntegrated <- FindClusters(MyeloidIntegrated, resolution = 0.3)
MyeloidIntegrated <- FindClusters(MyeloidIntegrated, resolution = 0.2)
MyeloidIntegrated <- FindClusters(MyeloidIntegrated, resolution = 0.1)
MyeloidIntegrated <- FindClusters(MyeloidIntegrated, resolution = 0.05)
message("FindClusters complete. Beginning UMAPs")


# Umaps
dim_plots <- list(
  DimPlot_clusters0.5 = DimPlot(MyeloidIntegrated, reduction = "umap", group.by = "integrated_snn_res.0.5") + ggtitle("Resolution 0.5"),
  DimPlot_clusters0.1 = DimPlot(MyeloidIntegrated, reduction = "umap", group.by = "integrated_snn_res.0.1") + ggtitle("Resolution 0.1"),
  DimPlot_clusters0.05 = DimPlot(MyeloidIntegrated, reduction = "umap", group.by = "integrated_snn_res.0.05") + ggtitle("Resolution 0.05"),
  DimPlot_clusters0.3 = DimPlot(MyeloidIntegrated, reduction = "umap", group.by = "integrated_snn_res.0.3") + ggtitle("Resolution 0.3"),
  DimPlot_clusters0.2 = DimPlot(MyeloidIntegrated, reduction = "umap", group.by = "integrated_snn_res.0.2") + ggtitle("Resolution 0.2")
)

message("UMAPs created!")

#Saving the UMAPs

#PDF
for (plot_name in names(dim_plots)) {
  ggsave(paste0(plot_name, ".pdf"), 
         plot = dim_plots[[plot_name]], 
         width = 8, height = 6)}

#PNG
for (plot_name in names(dim_plots)) {
  ggsave(paste0(plot_name, ".png"), 
         plot = dim_plots[[plot_name]], 
         width = 8, height = 6)}

message("UMAPs saved")

MyeloidIntegrated <- PrepSCTFindMarkers(MyeloidIntegrated)

#FindAllMarkers
Markers0.5 <- FindAllMarkers(MyeloidIntegrated, assay = "SCT", min.pct = 0.25, logfc.threshold = 0.25, group.by = "integrated_snn_res.0.5")
write_xlsx(Markers0.5,"/home/gabriel.batzli/jamie_project/Markers_0.5.xlsx",col_names = TRUE,format_headers = TRUE)

Markers0.1 <- FindAllMarkers(MyeloidIntegrated, assay = "SCT", min.pct = 0.25, logfc.threshold = 0.25, group.by = "integrated_snn_res.0.1")
write_xlsx(Markers0.1,"/home/gabriel.batzli/jamie_project/Markers_0.1.xlsx",col_names = TRUE,format_headers = TRUE)

Markers0.05 <- FindAllMarkers(MyeloidIntegrated, assay = "SCT", min.pct = 0.25, logfc.threshold = 0.25, group.by = "integrated_snn_res.0.05")
write_xlsx(Markers0.05,"/home/gabriel.batzli/jamie_project/Markers_0.05.xlsx",col_names = TRUE,format_headers = TRUE)
message("Find All Markers Finished and Saved")

write_xlsx(Markers0.2,"Markers_0.2.xlsx",col_names = TRUE,format_headers = TRUE)

saveRDS(MyeloidIntegrated, "/Users/jamiechoe/Desktop/PracticeRNA/jamie_project/Myeloid_Subcluster/Myeloid_Integrated.rds")

SaveSeuratRds(MyeloidIntegrated)
```

## QC Plot

Displays the nFeatures, nCount, and percent mitochondrial genes. Acts as quality control.

orig.ident - The project name you passed in the project = argument nCount_RNA - The total number of RNA molecules detected in the cell nFeature_RNA - The number of unique genes detected in the cell

```{r}
VlnPlot(MyeloidIntegrated, features = c("nFeature_RNA", "nCount_RNA", "percent.mt"), ncol = 3) 
```

## Analyzing MyeloidIntegrated

#### Mac 1 - SOD2

```{r}
FeaturePlot(MyeloidIntegrated, features = "SOD2", cols = c("lightgrey","#d49200"),min.cutoff = 0, max.cutoff = 4)
```

#### Mac 2 - C1QA

```{r}
FeaturePlot(MyeloidIntegrated, features = "C1QA",cols = c("lightgrey","#94aa01"),min.cutoff = 0, max.cutoff = 4)
```

#### cDC1 - CLEC9A

```{r}
FeaturePlot(MyeloidIntegrated, features = "CLEC9A",cols = c("lightgrey","#027661"),min.cutoff = 0, max.cutoff = 4)
```

#### cDC2 - CD1C

```{r}
FeaturePlot(MyeloidIntegrated, features = "CD1C",cols = c("#eeeeee","#f7766dff"),min.cutoff = 0, max.cutoff = 4)
```

#### DC3 - LAMP3

```{r}
FeaturePlot(MyeloidIntegrated, features = "LAMP3",cols = c("#eeeeee","#00bae3"),min.cutoff = 0, max.cutoff = 4)
```

#### pDC - MZB1

```{r}
FeaturePlot(MyeloidIntegrated, features = "MZB1",cols = c("#eeeeee","#db71fb"),min.cutoff = 0, max.cutoff = 4)
```

#### langerhans - CD207

```{r}
FeaturePlot(MyeloidIntegrated, features = "CD207",cols = c("lightgrey","#9591fc"),min.cutoff = 0, max.cutoff = 4)
```

#### Monocytes - FCN1

```{r}
FeaturePlot(MyeloidIntegrated, features = "FCN1",cols = c("lightgrey","#03c17d"),min.cutoff = 0, max.cutoff = 4)
```

## UMAP TIME

```{r}
#Subsetting Doublets out
MyeloidSinglets = subset(MyeloidIntegrated, idents = c("0","1","2","4","5","6","7","8"))
```

```{r}
Labeled_UMAP.ids <- c("cDC2","Mac 2","Mac 1","Monocytes","cDC1","DC3","Langerhans","pDC")
names(Labeled_UMAP.ids) <- levels(MyeloidSinglets)
MyeloidSinglets <- RenameIdents(MyeloidSinglets, Labeled_UMAP.ids)
DimPlot(MyeloidSinglets, reduction = "umap", label = TRUE, pt.size = 0.5) + NoLegend()
ggsave(filename = "LabeledUMAPMyeloid.png", height = 4, width = 8)
```

## Bubble Plot

```{r}
markers.to.plot <- c("IL23A",
"ALOX15",
"CD1C",
"PTTG1",
"AREG",
"CCL18",
"MAMDC2",
"CCL13",
"LYVE1",
"RAB3IL1",
"HEY1",
"CCL20",
"KANK1",
"SERPINB2",
"CRADD",
"FAM83F",
"FERMT1",
"AHNAK2",
"RP11-191L9.4",
"NECTIN4",
"PLAC8",
"FPR2",
"S100A12",
"THBS1",
"FCN1",
"CLEC9A",
"XCR1",
"PPY",
"PAK3",
"LINC01724",
"TREML1",
"ADAM12",
"CCDC68",
"SYNPO",
"UBD",
"RP11-597D13.8",
"IL22RA2",
"CHAD",
"SLC27A2",
"CD207",
"PTCRA",
"IGLC3",
"MZB1",
"JCHAIN",
"GZMB",
"LINC01436",
"MEG8",
"F10",
"WIF1",
"HAS2")

Idents(MyeloidIntegrated) <- factor(Idents(MyeloidIntegrated), levels = c("0", "1", "2", "3","4","5","6","7","8","9"))



MachroDot <- DotPlot(MyeloidIntegrated, features = markers.to.plot, dot.scale = 10, cols = c("white", "maroon")) + RotatedAxis()
MachroDot
```

## Violin Plot

```{r}
Idents(MyeloidSinglets) <- factor(Idents(MyeloidSinglets), levels = c("Mac 1","Mac 2","Monocytes","cDC2","DC3","cDC1","pDC","Langerhans"))

violin_genes_myeloid = c("CCL20","C1QA","FCN1","CD1C","LAMP3","CLEC9A","MZB1","CD207")
VlnPlot(object = MyeloidSinglets, features = violin_genes_myeloid, stack = TRUE)
```

------------------------------------------------------------------------

# Macrophage

## Pre-processing

```{r}
library(Seurat)
library(tidyverse)
library(dplyr)
library(patchwork)
library(SeuratObject)

MacroCluster <- subset(x = MyeloidIntegrated, idents = c("Mac 1","Mac 2"))

MacroCluster <- SplitObject(MacroCluster, split.by = "day")

#Using SCTransform on each object
MacroCluster <- lapply(MacroCluster, SCTransform, vst.flavor = "v2")
message("SCTransform Finished!")

#Integration
features <- SelectIntegrationFeatures(MacroCluster, nfeatures = 3000)
MacroCluster <- PrepSCTIntegration(MacroCluster, anchor.features = features)
message("Integration prepped, finding anchors now.")

#Anchors
DonorAnchors <- FindIntegrationAnchors(MacroCluster, normalization.method = "SCT", anchor.features = features)
#saveRDS(DonorAnchors, "/directory")
message("Anchors made and saved")

MacroCluster <- IntegrateData(anchorset = DonorAnchors, normalization.method = "SCT")
message("Integration complete.")

#Run PCA to find PCs
MacroCluster <- RunPCA(MacroCluster)
#saveRDS(MacroCluster, "/directory")
message("Finished running PCA")

#Creating Elbowplot
ElbowPlot(MacroCluster)
#ggsave("/directory", plot = EP, width = 8, height = 6)
message("Elbowplot created and saved")

SaveSeuratRds(MacroCluster)
saveRDS(MacroCluster, "/Users/jamiechoe/Desktop/PracticeRNA/jamie_project/Macro_subcluster/Merged_Donors.rds")
```

```{r}
library(openxlsx)
library(openxlsx) 
library(Seurat)
library(tidyverse)
library(patchwork)
library(sctransform)
library(ggplot2)
message("libs loaded")

# Process the data

MacroCluster <- RunUMAP(MacroCluster, reduction = "pca", dims = 1:11)

MacroCluster <- FindNeighbors(MacroCluster, reduction = "pca", dims = 1:11)

#Resolutions 
MacroCluster <- FindClusters(MacroCluster, resolution = 0.5)
MacroCluster <- FindClusters(MacroCluster, resolution = 0.1)
MacroCluster <- FindClusters(MacroCluster, resolution = 0.2)
MacroCluster <- FindClusters(MacroCluster, resolution = 0.3)
MacroCluster <- FindClusters(MacroCluster, resolution = 0.05)


# Umaps
dim_plots <- list(
  DimPlot_clusters0.5 = DimPlot(MacroCluster, reduction = "umap", group.by = "integrated_snn_res.0.5") + ggtitle("Resolution 0.5"),
  DimPlot_clusters0.1 = DimPlot(MacroCluster, reduction = "umap", group.by = "integrated_snn_res.0.1") + ggtitle("Resolution 0.1"),
  DimPlot_clusters0.05 = DimPlot(MacroCluster, reduction = "umap", group.by = "integrated_snn_res.0.05") + ggtitle("Resolution 0.05"),
  DimPlot_clusters0.2 = DimPlot(MacroCluster, reduction = "umap", group.by = "integrated_snn_res.0.2") + ggtitle("Resolution 0.2"),
  DimPlot_clusters0.3 = DimPlot(MacroCluster, reduction = "umap", group.by = "integrated_snn_res.0.3") + ggtitle("Resolution 0.3")
)

message("UMAPs created!")

#Saving the UMAPs

#PDF
for (plot_name in names(dim_plots)) {
  ggsave(paste0(plot_name, ".pdf"), 
         plot = dim_plots[[plot_name]], 
         width = 8, height = 6)}

#PNG
for (plot_name in names(dim_plots)) {
  ggsave(paste0(plot_name, ".png"), 
         plot = dim_plots[[plot_name]], 
         width = 8, height = 6)}

message("UMAPs saved")

MacroCluster <- PrepSCTFindMarkers(MacroCluster)

#FindAllMarkers
Markers0.5 <- FindAllMarkers(MacroCluster, assay = "SCT", min.pct = 0.25, logfc.threshold = 0.25, group.by = "integrated_snn_res.0.5")
write.xlsx(Markers0.5,"/Users/jamiechoe/Desktop/PracticeRNA/jamie_project/Macro_subcluster/MacroMarkers_0.5.xlsx")

Markers0.1 <- FindAllMarkers(MacroCluster, assay = "SCT", min.pct = 0.25, logfc.threshold = 0.25, group.by = "integrated_snn_res.0.1")
write.xlsx(Markers0.1,"/Users/jamiechoe/Desktop/PracticeRNA/jamie_project/Macro_subcluster/MacroMarkers_0.1.xlsx")

Markers0.05 <- FindAllMarkers(MacroCluster, assay = "SCT", min.pct = 0.25, logfc.threshold = 0.25, group.by = "integrated_snn_res.0.05")
write.xlsx(Markers0.05,"/Users/jamiechoe/Desktop/PracticeRNA/jamie_project/Macro_subcluster/MacroMarkers_0.05.xlsx")
message("Find All Markers Finished and Saved")


Markers0.3 <- FindAllMarkers(MacroCluster, assay = "SCT", min.pct = 0.25, logfc.threshold = 0.25, group.by = "integrated_snn_res.0.3", only.pos = TRUE)
write.xlsx(Markers0.3,"/Users/jamiechoe/Desktop/PracticeRNA/jamie_project/Macro_subcluster/MacroMarkers_0.3.xlsx")


#Save Object
saveRDS(MacroCluster,"/Users/jamiechoe/Desktop/PracticeRNA/jamie_project/Macro_subcluster/MacroCluster.rds")

message("obj saved")
```

## QC Plot

```{r}
VlnPlot(MacroCluster, features = c("nFeature_RNA", "nCount_RNA", "percent.mt"), ncol = 3) 
```

## Analyzing MacroCluster

### FeaturePlots

Macrophage 1 - IL1B

```{r}
FeaturePlot(MacroCluster, features = c("IL1B"),  cols = c("lightgrey","#94aa01ff"),min.cutoff = 0, max.cutoff = 4)
```

Early Macrophage 1 - G0S2

```{r}
FeaturePlot(MacroCluster, features = c("G0S2"),  cols = c("lightgrey","#00bae3ff"),min.cutoff = 0, max.cutoff = 4)
```

Macrophage 2 - C1QB

```{r}
FeaturePlot(MacroCluster, features = c("C1QB"),  cols = c("lightgrey","#f7766dff"),min.cutoff = 0, max.cutoff = 4)
```

Early Macrophage 2 - HSPA1B

```{r}
FeaturePlot(MacroCluster, features = c("HSPA1B"),  cols = c("lightgrey","#db71fbff"),min.cutoff = 0, max.cutoff = 4)
```

### UMAP TIME

```{r}
Labeled_UMAP.ids <- c("Mac 2","Mac 1","Early Mac 1","Transitioning Mac")
names(Labeled_UMAP.ids) <- levels(MacroCluster)
Merged_Donors <- RenameIdents(MacroCluster, Labeled_UMAP.ids)
DimPlot(Merged_Donors, reduction = "umap", label = TRUE, pt.size = 0.5) + NoLegend()
ggsave(filename = "/Users/jamiechoe/Desktop/PracticeRNA/jamie_project/Macro_subcluster/LabeledMacroUMAP.png", height = 4, width = 8)
```

### DotPlot

```{r}
library(ggplot2)

markers.to.plot <- c("C1QB", "RNASE1", "CCL13",
                     "SEMA3C", "IL1B", "CCL20",
                     "G0S2", "LYZ", "SERPINB9",
                     "DNAJB1", "JUN", "HSPA1B")

# Extract DotPlot data
dot_data <- DotPlot(MacroCluster, features = markers.to.plot, dot.scale = 10)$data

# Assign gene colors (for outline)
gene_outline_colors <- c(rep("#f7766dff", 3),
                         rep("#94aa01ff", 3),
                         rep("#00bae3ff", 3),
                         rep("#db71fbff", 3))
names(gene_outline_colors) <- markers.to.plot

# Add color column to the data
dot_data$outline_color <- gene_outline_colors[dot_data$features.plot]

# Plot: fill = avg.exp (gradient), color = gene-based outline
MacroDot <- ggplot(dot_data, aes(x = id, y = features.plot, size = pct.exp)) +
  geom_point(aes(fill = avg.exp, color = outline_color), shape = 21, stroke = 1.2) +
  scale_fill_gradient(low = "white", high = "black") +
  scale_color_identity() +
  scale_size(range = c(0, 10)) +
  theme_minimal() +
  xlab("Cluster") + ylab("Gene") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggsave(filename = "/Users/jamiechoe/Desktop/PracticeRNA/jamie_project/Macro_subcluster/MacroDotPlot.png", height = 4, width = 8)

MacroDot
```

###StackedBarplot

```{r}
library(Seurat)
library(dplyr)
library(ggplot2)

# Step 1: Extract metadata with identities and timepoints
meta_df <- MacroCluster@meta.data %>%
  dplyr::select(cell_type = seurat_clusters, timepoint = day)  # Change to your actual timepoint column

# Step 2: Count cells per cell type and timepoint
cell_counts <- meta_df %>%
  group_by(timepoint, cell_type) %>%
  summarise(n = n()) %>%
  mutate(percent = n / sum(n) * 100)

# Step 3: Plot
StackedbarplotMacro = ggplot(cell_counts, aes(x = timepoint, y = percent, fill = cell_type)) +
  geom_bar(stat = "identity", position = "stack") +
  labs(x = "Timepoint", y = "Percent of Cells", fill = "Cell Type") +
  theme_minimal() +
  scale_fill_manual(values = c("#f7766dff","#94aa01ff","#00bae3ff","#db71fbff"))

ggsave(filename = "/Users/jamiechoe/Desktop/PracticeRNA/jamie_project/Macro_subcluster/MacroStackedBarplot.png", height = 8, width = 4)

StackedbarplotMacro
```

### UMAP by Day

```{r}
MacroCluster$day <- ifelse(grepl("Day0", MacroCluster$orig.ident), "D0", "D1")

# Confirm it worked:
table(MacroCluster$day)

DimPlot(MacroCluster, group.by = "day", label = TRUE) + ggtitle("D0 vs. D1")
```

------------------------------------------------------------------------

# Fibroblast

## Pre-processing

```{r}
library(Seurat)
library(tidyverse)
library(dplyr)
library(patchwork)
library(SeuratObject)

#Merged_Donors <- readRDS("/home/gabriel.batzli/jamie_project/Merged_Donors_Object.rds")

#Subsetting from Merged Donors to isolate Myeloid cluster
FibroCluster <- subset(x = Merged_Donors, idents = c("Fibroblasts"))

FibroCluster <- SplitObject(FibroCluster, split.by = "day")

#Using SCTransform
FibroCluster <- lapply(FibroCluster, SCTransform, vst.flavor = "v2")
message("SCTransform Finished!")

#Integration
features <- SelectIntegrationFeatures(object.list = FibroCluster, nfeatures = 3000)
FibroCluster <- PrepSCTIntegration(object.list = FibroCluster, anchor.features = features)
message("Integration prepped, finding anchors now.")

#Anchors
DonorAnchors <- FindIntegrationAnchors(object.list = FibroCluster, normalization.method = "SCT", anchor.features = features)
#saveRDS(DonorAnchors, "/home/gabriel.batzli/jamie_project/Myeloid_Anchors.rds")
message("Anchors made and saved")

FibroCluster <- IntegrateData(anchorset = DonorAnchors, normalization.method = "SCT")
message("Integration complete.")


#Run PCA to find PCs
FibroCluster <- RunPCA(FibroCluster)
#saveRDS(FibroCluster, "/home/gabriel.batzli/jamie_project/Myeloid_Cluster_Object.rds")
message("Finished running PCA")

#Creating Elbowplot
ElbowPlot(FibroCluster)
```

```{r}
install.packages("openxlsx", dependencies = TRUE)
library(openxlsx)
library(writexl)


# Process the data

FibroCluster <- RunUMAP(FibroCluster, reduction = "pca", dims = 1:11)

FibroCluster <- FindNeighbors(FibroCluster, reduction = "pca", dims = 1:11)


#Resolutions 
FibroCluster <- FindClusters(FibroCluster, resolution = 0.5)
FibroCluster <- FindClusters(FibroCluster, resolution = 0.3)
FibroCluster <- FindClusters(FibroCluster, resolution = 0.2)
FibroCluster <- FindClusters(FibroCluster, resolution = 0.1)
message("FindClusters complete. Beginning UMAPs")


# Umaps
dim_plots <- list(
  DimPlot_clusters0.5 = DimPlot(FibroCluster, reduction = "umap", group.by = "integrated_snn_res.0.5") + ggtitle("Resolution 0.5"),
  DimPlot_clusters0.1 = DimPlot(FibroCluster, reduction = "umap", group.by = "integrated_snn_res.0.1") + ggtitle("Resolution 0.1"),
  DimPlot_clusters0.05 = DimPlot(FibroCluster, reduction = "umap", group.by = "integrated_snn_res.0.05") + ggtitle("Resolution 0.05"),
  DimPlot_clusters0.3 = DimPlot(FibroCluster, reduction = "umap", group.by = "integrated_snn_res.0.3") + ggtitle("Resolution 0.3"),
  DimPlot_clusters0.2 = DimPlot(FibroCluster, reduction = "umap", group.by = "integrated_snn_res.0.2") + ggtitle("Resolution 0.2")
)

```

## Analyzing Fibroblast

### FindAllMarkers

```{r}
FibroCluster <- PrepSCTFindMarkers(FibroCluster)
FibroMarkers0.5 <- FindAllMarkers(FibroCluster, assay = "SCT", min.pct = 0.25, logfc.threshold = 0.25, group.by = "integrated_snn_res.0.5")
write_xlsx(FibroMarkers0.5,"/Users/jamiechoe/Desktop/PracticeRNA/jamie_project/Fibroblasts_Subcluster/FibroMarkers_0.5.xlsx",col_names = TRUE,format_headers = TRUE)

FibroMarkers0.5
```

### FeaturePlots

FB-II (C3, CCL19)

```{r}
FeaturePlot(FibroCluster, features = "C3", cols = c("lightgrey", "#f7766dff"))
```

FB-II (APOD, ITM2A)

```{r}
FeaturePlot(FibroCluster, features = "APOD", cols = c("lightgrey","#d49200ff"))
```

Reticular (FBLN1)

```{r}
FeaturePlot(FibroCluster, features = "FBLN1", cols = c("lightgrey","#94aa01ff"))
```

FB-III (COL2341, LEPR)

```{r}
FeaturePlot(FibroCluster, features = "LEPR", cols = c("lightgrey","#03bb38ff"))
```

FB-III (LEPR, WIf1)

```{r}
FeaturePlot(FibroCluster, features = "WIF1", cols = c("lightgrey","#db71fbff"))
```

FB-I (COMP+)

```{r}
FeaturePlot(FibroCluster, features = "COMP", cols = c("lightgrey","#00bae3ff"))
```

FB-I (COL11A1+)

```{r}
FeaturePlot(FibroCluster, features = "COL11A1", cols = c("lightgrey","#629dffff"))
```

###UMAP

```{r}
#Filtering Out Singlets
FibroSinglets = subset(FibroCluster, idents = c("0","1","2","3","4","5","6"))

RunUMAP(FibroSinglets, dims = 1:15, reduction = "pca") 
DimPlot(FibroSinglets, reduction = "umap")#Creates UMAP with 1:15 PCs. 
ggsave(filename = "/Users/jamiechoe/Desktop/PracticeRNA/jamie_project/Fibroblasts_Subcluster/UMAP.Fibro.png", height = 8, width = 4)
```

### Violin Plot

```{r}
violin_genes = c("CCL19","APOD","FBLN1","LEPR","COMP","COL11A1","WIf1")
VlnPlot(object = FibroSinglets, features = violin_genes, stack = TRUE)
```

### Stacked Barplot

```{r}
library(Seurat)
library(dplyr)
library(ggplot2)

# Step 1: Extract metadata with identities and timepoints
meta_df <- FibroSinglets@meta.data %>%
  dplyr::select(cell_type = seurat_clusters, timepoint = day)  # Change to your actual timepoint column

# Step 2: Count cells per cell type and timepoint
cell_counts <- meta_df %>%
  group_by(timepoint, cell_type) %>%
  summarise(n = n()) %>%
  mutate(percent = n / sum(n) * 100)

# Step 3: Plot
StackedbarplotFibro = ggplot(cell_counts, aes(x = timepoint, y = percent, fill = cell_type)) +
  geom_bar(stat = "identity", position = "stack") +
  labs(x = "Timepoint", y = "Percent of Cells", fill = "Cell Type") +
  theme_minimal() +
  scale_fill_manual(values = c("#f7766dff","#d49200ff","#94aa01ff","#03bb38ff","#00bae3ff","#629dffff","#db71fbff"))

ggsave(filename = "/Users/jamiechoe/Desktop/PracticeRNA/jamie_project/Fibroblasts_Subcluster/FibroStackedBarplot.png", height = 8, width = 4)

StackedbarplotFibro
```

# Macro/Mono

## Pre-processing

```{r}
library(Seurat)
library(tidyverse)
library(dplyr)
library(patchwork)
library(SeuratObject)

MacroMono <- subset(x = MyeloidSinglets, idents = c("Mac 1","Mac 2", "Monocytes"))

MacroMono <- SplitObject(MacroMono, split.by = "day")

#Using SCTransform on each object
MacroMono <- lapply(MacroMono, SCTransform, vst.flavor = "v2")
message("SCTransform Finished!")

#Integration
features <- SelectIntegrationFeatures(MacroMono, nfeatures = 3000)
MacroMono <- PrepSCTIntegration(MacroMono, anchor.features = features)
message("Integration prepped, finding anchors now.")

#Anchors
DonorAnchors <- FindIntegrationAnchors(MacroMono, normalization.method = "SCT", anchor.features = features)
#saveRDS(DonorAnchors, "/directory")
message("Anchors made and saved")

MacroMono <- IntegrateData(anchorset = DonorAnchors, normalization.method = "SCT")
message("Integration complete.")

#Run PCA to find PCs
MacroMono <- RunPCA(MacroMono)
#saveRDS(MacroMono, "/directory")
message("Finished running PCA")

#Creating Elbowplot
ElbowPlot(MacroMono)
#ggsave("/directory", plot = EP, width = 8, height = 6)
message("Elbowplot created and saved")

SaveSeuratRds(MacroMono)
```

```{r}
library(openxlsx)
library(openxlsx) 
library(Seurat)
library(tidyverse)
library(patchwork)
library(sctransform)
library(ggplot2)
message("libs loaded")

# Process the data

MacroMono <- RunUMAP(MacroMono, reduction = "pca", dims = 1:9)

MacroMono <- FindNeighbors(MacroMono, reduction = "pca", dims = 1:9)

#Resolutions 
MacroMono <- FindClusters(MacroMono, resolution = 0.5)
MacroMono <- FindClusters(MacroMono, resolution = 0.1)
MacroMono <- FindClusters(MacroMono, resolution = 0.2)
MacroMono <- FindClusters(MacroMono, resolution = 0.35)
MacroMono <- FindClusters(MacroMono, resolution = 0.05)





DimPlot_clusters0.5 = DimPlot(MacroMono, reduction = "umap", group.by = "integrated_snn_res.0.5") + ggtitle("Resolution 0.5")
DimPlot_clusters0.1 = DimPlot(MacroMono, reduction = "umap", group.by = "integrated_snn_res.0.1") + ggtitle("Resolution 0.1")
DimPlot_clusters0.05 = DimPlot(MacroMono, reduction = "umap", group.by = "integrated_snn_res.0.05") + ggtitle("Resolution 0.05")
DimPlot_clusters0.2 = DimPlot(MacroMono, reduction = "umap", group.by = "integrated_snn_res.0.2") + ggtitle("Resolution 0.2")
DimPlot_clusters0.35 = DimPlot(MacroMono, reduction = "umap", group.by = "integrated_snn_res.0.35") + ggtitle("Resolution 0.35")
DimPlot_clusters0.4 = DimPlot(MacroMono, reduction = "umap", group.by = "integrated_snn_res.0.4") + ggtitle("Resolution 0.4")

DimPlot_clusters0.3
DimPlot_clusters0.5
DimPlot_clusters0.1
DimPlot_clusters0.05
DimPlot_clusters0.2
DimPlot_clusters0.4
DimPlot_clusters0.35
message("UMAPs created!")

#Saving the UMAPs

#PDF
for (plot_name in names(dim_plots)) {
  ggsave(paste0(plot_name, ".pdf"), 
         plot = dim_plots[[plot_name]], 
         width = 8, height = 6)}

#PNG
for (plot_name in names(dim_plots)) {
  ggsave(paste0(plot_name, ".png"), 
         plot = dim_plots[[plot_name]], 
         width = 8, height = 6)}

message("UMAPs saved")

####IMPORTANT!! JAMIE DO NOT FORGET####
MacroMono <- PrepSCTFindMarkers(MacroMono)

#FindAllMarkers
Markers0.5 <- FindAllMarkers(MacroMono, assay = "SCT", min.pct = 0.25, logfc.threshold = 0.25, group.by = "integrated_snn_res.0.5", only.pos = TRUE)
write.xlsx(Markers0.5,"/Users/jamiechoe/Desktop/PracticeRNA/jamie_project/MacroMono_Subcluster/Markers_0.5MacroMono.xlsx")

Markers0.1 <- FindAllMarkers(MacroMono, assay = "SCT", min.pct = 0.25, logfc.threshold = 0.25, group.by = "integrated_snn_res.0.1")
write.xlsx(Markers0.1,"/home/gabriel.batzli/jamie_project/Markers_0.1.xlsx")

Markers0.05 <- FindAllMarkers(MacroMono, assay = "SCT", min.pct = 0.25, logfc.threshold = 0.25, group.by = "integrated_snn_res.0.05")
write.xlsx(Markers0.05,"/home/gabriel.batzli/jamie_project/Markers_0.05.xlsx")
message("Find All Markers Finished and Saved")


Markers0.35 <- FindAllMarkers(MacroMono, assay = "SCT", min.pct = 0.25, logfc.threshold = 0.25, group.by = "integrated_snn_res.0.35", only.pos = TRUE)
write.xlsx(Markers0.35,"/Users/jamiechoe/Desktop/PracticeRNA/jamie_project/MacroMono_Subcluster/Markers_0.35MacroMono.xlsx")


Markers0.3 <- FindAllMarkers(MacroMono, assay = "SCT", min.pct = 0.25, logfc.threshold = 0.25, group.by = "integrated_snn_res.0.3", only.pos = TRUE)
write.xlsx(Markers0.3,"MacroMarkers_0.3.xlsx")


#Save Object
saveRDS(MacroMono,"MacroMono.rds")

message("obj saved")
```

##FeaturePlots

```{r}
FeaturePlot(MacroMono, features = "ISG15", min.cutoff = 0)
```

```{r}
FeaturePlot(MacroMono, features = "ISG20", min.cutoff = 0)
```

```{r}
FeaturePlot(MacroMono, features = "PLAC8")
```

```{r}
FeaturePlot(MacroMono, features = "S100A8")
```

```{r}
FeaturePlot(MacroMono, features = "S100A9")
```

## StackedBarplot

```{r}
library(Seurat)
library(dplyr)
library(ggplot2)

#Extract metadata with identities and timepoints
meta_df <- MacroMono@meta.data %>%
  dplyr::select(cell_type = seurat_clusters, timepoint = day)  # Change to your actual timepoint column

#Count cells per cell type and timepoint
cell_counts <- meta_df %>%
  group_by(timepoint, cell_type) %>%
  summarise(n = n()) %>%
  mutate(percent = n / sum(n) * 100)

# Stacked BarPlot
StackedbarplotMacMono = ggplot(cell_counts, aes(x = timepoint, y = percent, fill = cell_type)) +
  geom_bar(stat = "identity", position = "stack") +
  labs(x = "Timepoint", y = "Percent of Cells", fill = "Cell Type") +
  theme_minimal() +
  scale_fill_manual(values = c("#f7766dff","#d49200ff","#03bb38ff","#00bae3ff","#629dffff","#db71fbff"))
```

## UMAP

```{r}
Labeled_UMAP.ids <- c("C1Q Hi","M1-like","VEGFA Hi","Monocytes","M2-like","Early M2-like")
names(Labeled_UMAP.ids) <- levels(MacroMono)
MacroMono <- RenameIdents(MacroMono, Labeled_UMAP.ids)
DimPlot(MacroMono, reduction = "umap", label = TRUE, pt.size = 0.5) + NoLegend()
ggsave(filename = "LabeledUMAP.png", height = 4, width = 8)
```
