---
title: "MergedSeurat+CellChat"
output: html_document
date: "2025-07-22"
---

```{r}
library(seurat)
library(CellChat)
```

#Preparing Seurat Objects

##Splitting Fibroblasts and MacroMono by day
```{r setup, include=FALSE}
#Fibroblasts
FibroDay0 = subset(FibroSinglets, subset = day == "D0")
FibroDay1 = subset(FibroSinglets, subset = day == "D1")

#MacroMono
MacroMonoD0 = subset(MacroMono, subset = day == "D0")
MacroMonoD1 = subset(MacroMono, subset = day == "D1")

```

##Setting Idents to metadata
```{r}
#Adds Idents to CellType metadata
FibroDay0$CellType <- Idents(FibroDay0)
FibroDay1$CellType <- Idents(FibroDay1)

MacroMonoD0$CellType <- Idents(MacroMonoD0)
MacroMonoD1$CellType <- Idents(MacroMonoD1)
```

##Merging together Fibro and Macro into one seurat object
```{r}
#Day 0 
FibroMacroD0 <- merge(
  x = FibroDay0,
  y = MacroMonoD0,
  add.cell.ids = c("Fibro","Macro"),
  project = "PatientMerge") 

#Day 1
FibroMacroD1 <- merge(
  x = FibroDay1,
  y = MacroMonoD1,
  add.cell.ids = c("Fibro","Macro"),
  project = "PatientMerge") 
```

#D0 cellchat object
```{r}
data.input <- FibroMacroD0[["SCT"]]@data # normalized data matrix
labels <- Idents(FibroMacroD0)
# create a dataframe of the cell labels
meta <- data.frame(labels = labels, row.names = names(labels)) 
```


```{r}
#Creating CellChat Object
FibroMacroChatD0 <- createCellChat(object = FibroMacroD0, group.by = "ident", assay = "SCT")
```
```{r}
FibroMacroChatD0 <- addMeta(FibroMacroChatD0, meta = meta)
#set "labels" as default cell identity
FibroMacroChatD0 <- setIdent(FibroMacroChatD0, ident.use = "labels") 

#show factor levels of the cell labels
levels(FibroMacroChatD0@idents) 

#number of cells in each cell group
groupSize <- as.numeric(table(FibroMacroChatD0@idents)) 
```

```{r}
CellChatDB <- CellChatDB.human # Uses CellChatDB from human 
showDatabaseCategory(CellChatDB)

# use a subset of CellChatDB for cell-cell communication analysis
CellChatDB.use <- subsetDB(CellChatDB, search = "Secreted Signaling", key = "annotation") # use Secreted Signaling

# set the used database in the object
FibroMacroChatD0@DB <- CellChatDB.use
```

```{r}
# subset the expression data of signaling genes for saving computation cost
FibroMacroChatD0 <- subsetData(FibroMacroChatD0) 
future::plan("multisession", workers = 4) # do parallel processing
FibroMacroChatD0 <- identifyOverExpressedGenes(FibroMacroChatD0)
FibroMacroChatD0 <- identifyOverExpressedInteractions(FibroMacroChatD0)

ptm = Sys.time()
execution.time = Sys.time() - ptm
print(as.numeric(execution.time, units = "secs"))
```

```{r}
ptm = Sys.time()
FibroMacroChatD0 <- computeCommunProb(FibroMacroChatD0, type = "triMean")
```

```{r}
#Filters out communications between less than 10 cells
FibroMacroChatD0 <- filterCommunication(FibroMacroChatD0, min.cells = 10) #not sure if this is necessary

#computes the communication probability on signaling pathway level
FibroMacroChatD0 <- computeCommunProbPathway(FibroMacroChatD0)

#Calculate the aggregated cell-cell communication network
FibroMacroChatD0 <- aggregateNet(FibroMacroChatD0)
execution.time = Sys.time() - ptm
print(as.numeric(execution.time, units = "secs"))

#Saving the object
saveRDS(FibroMacroChatD0, file = "FibroMacroChatD0.rds")
```

```{r}
ptm = Sys.time()
groupSize <- as.numeric(table(FibroMacroChatD0@idents))
par(mfrow = c(1,2), xpd=TRUE)
netVisual_circle(FibroMacroChatD0@net$count, vertex.weight = groupSize, weight.scale = T, label.edge= F, title.name = "Number of interactions")
netVisual_circle(FibroMacroChatD0@net$weight, vertex.weight = groupSize, weight.scale = T, label.edge= F, title.name = "Interaction weights/strength")
```

```{r}
mat <- FibroMacroChatD0@net$weight

par(mfrow = c(3,4), xpd=TRUE)

suppressWarnings(for (i in 1:nrow(mat)) {
  mat2 <- matrix(0, nrow = nrow(mat), ncol = ncol(mat), dimnames = dimnames(mat))
  mat2[i, ] <- mat[i, ]
  netVisual_circle(mat2, vertex.weight = groupSize, weight.scale = T, edge.weight.max = max(mat), title.name = rownames(mat)[i])
})
```

```{r}
#Shows the available pathways 
FibroMacroChatD0@netP$pathways
```

##Heatmap
```{r}
#Sets which pathway to show
pathways.show <- c("CXCL") 

# Heatmap
par(mfrow=c(1,1))
netVisual_heatmap(FibroMacroChatD0, signaling = pathways.show, color.heatmap = "Reds")

```








#D1 Cellchat Object

```{r}
data.input <- FibroMacroD1[["SCT"]]@data # normalized data matrix
labels <- Idents(FibroMacroD1)
meta <- data.frame(labels = labels, row.names = names(labels)) # create a dataframe of the cell labels
```


```{r}
FibroMacroChatD1 <- createCellChat(object = FibroMacroD1, group.by = "ident", assay = "SCT")
```
```{r}
FibroMacroChatD1 <- addMeta(FibroMacroChatD1, meta = meta)
FibroMacroChatD1 <- setIdent(FibroMacroChatD1, ident.use = "labels") # set "labels" as default cell identity
levels(FibroMacroChatD1@idents) # show factor levels of the cell labels
groupSize <- as.numeric(table(FibroMacroChatD1@idents)) # number of cells in each cell group
```

```{r}
CellChatDB <- CellChatDB.human 
showDatabaseCategory(CellChatDB)

# use a subset of CellChatDB for cell-cell communication analysis
CellChatDB.use <- subsetDB(CellChatDB, search = "Secreted Signaling", key = "annotation") # use Secreted Signaling

# set the used database in the object
FibroMacroChatD1@DB <- CellChatDB.use
```

```{r}
# subset the expression data of signaling genes for saving computation cost
FibroMacroChatD1 <- subsetData(FibroMacroChatD1) # This step is necessary even if using the whole database
future::plan("multisession", workers = 4) # do parallel
FibroMacroChatD1 <- identifyOverExpressedGenes(FibroMacroChatD1)
FibroMacroChatD1 <- identifyOverExpressedInteractions(FibroMacroChatD1)

ptm = Sys.time()
execution.time = Sys.time() - ptm
print(as.numeric(execution.time, units = "secs"))
```

```{r}
ptm = Sys.time()
FibroMacroChatD1 <- computeCommunProb(FibroMacroChatD1, type = "triMean")
```

```{r}
#Filters out communications between less than 10 cells
FibroMacroChatD1 <- filterCommunication(FibroMacroChatD1, min.cells = 10)

#computes the communication probability on signaling pathway level
FibroMacroChatD1 <- computeCommunProbPathway(FibroMacroChatD1)

#Calculate the aggregated cell-cell communication network
FibroMacroChatD1 <- aggregateNet(FibroMacroChatD1)
execution.time = Sys.time() - ptm
print(as.numeric(execution.time, units = "secs"))

#Saving the object
saveRDS(FibroMacroChatD1, file = "FibroMacroChatD1.rds")
```


```{r}
#Show available pathways
FibroMacroChatD1@netP$pathways
```

##Heatmap
```{r}
#Sets which pathway to show
pathways.show <- c("VEGF") 

# Heatmap side by side between D0 and D1
par(mfrow=c(1,1))
netVisual_heatmap(FibroMacroChatD1, signaling = pathways.show, color.heatmap = "Reds") + 
  netVisual_heatmap(FibroMacroChatD0, signaling = pathways.show, color.heatmap = "Reds")
```









--------------------------------------------------------------------------------



#Merging CellChat D0 and D1 Objects
```{r}
#Computing centrality before merging!
netAnalysis_computeCentrality(FibroMacroChatD0)
FibroMacroChatD0 <- netAnalysis_computeCentrality(FibroMacroChatD0)

netAnalysis_computeCentrality(FibroMacroChatD1)
FibroMacroChatD1 <- netAnalysis_computeCentrality(FibroMacroChatD1)


object.list <- list(D0 = FibroMacroChatD0, D1 = FibroMacroChatD1)
FibroMacroChat <- mergeCellChat(object.list, add.names = names(object.list))


FibroMacroChat
```

```{r}
saveRDS(FibroMacroChat, file = "FibroMacroChat.rds")
```

##Compare the total number of interactions and interaction strength
```{r}
ptm = Sys.time()
gg1 <- compareInteractions(FibroMacroChat, show.legend = F, group = c(1,2))
gg2 <- compareInteractions(FibroMacroChat, show.legend = F, group = c(1,2), measure = "weight")
gg1 + gg2
```

```{r}
par(mfrow = c(1,2), xpd=TRUE)
netVisual_diffInteraction(FibroMacroChat, weight.scale = T)
netVisual_diffInteraction(FibroMacroChat, weight.scale = T, measure = "weight")
```



```{r}
# Chord diagram
pathways.show <- c("CXCL") 
par(mfrow = c(1,2), xpd=TRUE)
for (i in 1:length(object.list)) {
  netVisual_aggregate(object.list[[i]], signaling = pathways.show, layout = "chord", signaling.name = paste(pathways.show, names(object.list)[i]))
}
```

```{r}
weight.max <- getMaxWeight(object.list, attribute = c("idents","count"))
par(mfrow = c(1,2), xpd=TRUE)
suppressWarnings(for (i in 1:length(object.list)) {
  netVisual_circle(object.list[[i]]@net$count, weight.scale = T, label.edge= F, edge.weight.max = weight.max[2], edge.width.max = 12, title.name = paste0("Number of interactions - ", names(object.list)[i]))
})
```




```{r}
gg1 <- netAnalysis_signalingChanges_scatter(FibroMacroChat, idents.use = "Hypodermal", signaling.exclude = "Fascial")
#> Visualizing differential outgoing and incoming signaling changes from NL to LS
#> The following `from` values were not present in `x`: 0
#> The following `from` values were not present in `x`: 0, -1
gg2 <- netAnalysis_signalingChanges_scatter(FibroMacroChat, idents.use = "Hypodermal", signaling.exclude = c("Fascial"))
#> Visualizing differential outgoing and incoming signaling changes from NL to LS
#> The following `from` values were not present in `x`: 0, 2
#> The following `from` values were not present in `x`: 0, -1
patchwork::wrap_plots(plots = list(gg1,gg2))
```

##Outgoing Heatmaps
```{r}
library(ComplexHeatmap)

i = 1
# combining all the identified signaling pathways from different datasets 
pathway.union <- union(object.list[[i]]@netP$pathways, object.list[[i+1]]@netP$pathways)
ht1 = netAnalysis_signalingRole_heatmap(object.list[[i]], pattern = "outgoing", signaling = pathway.union, title = names(object.list)[i], width = 5, height =10, font.size = 5 )
ht2 = netAnalysis_signalingRole_heatmap(object.list[[i]], pattern = "incoming", signaling = pathway.union, title = names(object.list)[i], width = 5, height = 6)

draw(ht1 + ht2, ht_gap = unit(0.5, "cm"))

ht1

ht2
```

#Pathway interactions 

##CXCL

###CirclePlot
```{r}
pathways.show <- c("CXCL") 
weight.max <- getMaxWeight(object.list, slot.name = c("netP"), attribute = pathways.show) # control the edge weights across different datasets
par(mfrow = c(1,2), xpd=TRUE)
suppressWarnings(for (i in 1:length(object.list)) {
  netVisual_aggregate(object.list[[i]], signaling = pathways.show, layout = "circle", edge.weight.max = weight.max[1], edge.width.max = 10, signaling.name = paste(pathways.show, names(object.list)[i]))
})
```

###Heatmap
```{r}
pathways.show <- c("CXCL") 
par(mfrow = c(1,2), xpd=TRUE)
ht <- list()
for (i in 1:length(object.list)) {
  ht[[i]] <- netVisual_heatmap(object.list[[i]], signaling = pathways.show, color.heatmap = "Reds",title.name = paste(pathways.show, "signaling ",names(object.list)[i]))
}
#> Do heatmap based on a single object 
#> 
#> Do heatmap based on a single object
ComplexHeatmap::draw(ht[[1]] + ht[[2]], ht_gap = unit(0.5, "cm"))
```


```{r}
par(mfrow = c(1, 2), xpd = TRUE)
for (i in 1:length(object.list)) {
  netVisual_chord_gene(
    object.list[[i]],
    sources.use = "Papillary",
    targets.use = c("C1Q Hi", "M1-like", "VEGFA Hi", "Monocytes", "M2-like", "Early M2-like"),
    slot.name = "netP",
    title.name = paste0("Papillary → Macro/Monocytes - ", names(object.list)[i]),
    legend.pos.x = 10
  )
}

png("Papillary_to_MacroMonocytes.png", width = 2000, height = 1000, res = 300)


```


```{r}
netVisual_chord_gene(
  object.list[["D0"]],
  sources.use = "Papillary",
  targets.use = c("C1Q Hi", "M1-like", "VEGFA Hi", "Monocytes", "M2-like", "Early M2-like"),
  slot.name = "netP",
  title.name = "Papillary → Macro/Monocytes (Day 0)",
  legend.pos.x = 10
)
```













